---
title: "Use RApsimNG to modify apximx file"
author: "Bangyou Zheng"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette
vignette: |
  %\VignetteIndexEntry{RApsimNG} 
  %\VignetteEngine{knitr::rmarkdown} 
  %\VignetteEncoding{UTF-8}
---


The RApsimNG is designed to modify and run the *.apsimx simulations using R.


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(RApsimNG)
```


## Read APSIMX file

The `wheat.apsimx` in the validation dataset of APSIM NG  is used as an example. Function `read_apsimx` is used to read `*.apsimx` file through `jsonlite::read_json` and returns as a list.


```{r read-apsimx}
# Read Wheat.apsimx file with `read_apsimx` which returns a list of json results.
file <- system.file("wheat.apsimx", package = "RApsimNG")
m <- read_apsimx(file)

```

## Search by of APSIM NG 

A node can be found using the path style in APSIMX. 
```{r search-path}


```
## Modify and replace a model  

## Create a new model



